Reanalysis Step 3: Propensity Score Analysis with Twang

### 2025-08-19 reanalysis-3-propensity_scores.qmd
better diagnostic plots

  # Display twang diagnostic plots
  plot(twang_model)

  # Display balance summary
  print(summary(twang_model))
}
```

@@

```{r weight-stability}
if (avg_weights$Max_Weight_Overall > 10) {
  print("⚠ WARNING: Maximum weight > 10, indicating potential instability")
  print("Consider increasing n.trees or adjusting twang parameters")
} else if (avg_weights$Max_Weight_Overall > 5) {
  print("📊 NOTE: Maximum weight > 5, monitor for stability in outcome analysis")
} else {
  print("✓ GOOD: Weights appear stable (max < 5)")
}
```

>>>>

  # Plot 1: Iteration convergence
  cat("#### Convergence\n")
  plot(twang_model, plots = 1)

  # Plot 2: Boxplots of weights
  cat("\n#### Weight Distribution\n")
  plot(twang_model, plots = 2)

  # Plot 3: Balance reduction (standardized effect sizes)
  cat("\n#### Covariate Balance\n")
  plot(twang_model, plots = 3)

  # Plot 6: Proportion of weights histogram
  cat("\n#### Weight Proportions\n")
  plot(twang_model, plots = 6)

  # Display balance summary table
  cat("\n#### Balance Summary Table\n")
  print(summary(twang_model))
}
```

@@

```{r weight-stability}
if (avg_weights$Max_Weight_Overall > 10) {
  print("WARNING: Maximum weight > 10, indicating potential instability")
  print("Consider increasing n.trees or adjusting twang parameters")
} else {
  print("GOOD: Weights appear stable (max < 10)")
}
```
